Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-06-13 paper/paper.tex
Unnecessary word

In \cref{algorithm:mccis} we present a novel clique-inspired algorithm which finds a maximum common
connected induced subgraph isomorphism via an association graph. If the additional branching
restrictions are removed, the core of the algorithm is the same as the ``MCSa1'' clique algorithm
used in the previous section (and we refer the reader to the previously cited works for
implementation details on how to use bitsets and other data structures to implement the colouring
stage with very low constant factors). The way we extend this algorithm for connectedness differs
considerably from that of Koch \cite{DBLP:journals/tcs/Koch01} and Vismara and Valery
\cite{DBLP:conf/mco/VismaraV08}: these earlier approaches worked by classifying labels in the
association graph based upon whether a common vertex is shared, and then constructing cliques with
particular edge properties---this is harder to integrate with a strong bound function.

>>>>

In \cref{algorithm:mccis} we present a novel clique-inspired algorithm which finds a maximum common
connected induced subgraph via an association graph. If the additional branching
restrictions are removed, the core of the algorithm is the same as the ``MCSa1'' clique algorithm
used in the previous section (and we refer the reader to the previously cited works for
implementation details on how to use bitsets and other data structures to implement the colouring
stage with very low constant factors). The way we extend this algorithm for connectedness differs
considerably from that of Koch \cite{DBLP:journals/tcs/Koch01} and Vismara and Valery
\cite{DBLP:conf/mco/VismaraV08}: these earlier approaches worked by classifying labels in the
association graph based upon whether a common vertex is shared, and then constructing cliques with
particular edge properties---this is harder to integrate with a strong bound function.
